# Results of RGI-MOB-NF

Here is the start of the report.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(knitr)
df <- read_csv("results/All_samples.csv")

```

Amount of AMR genes detected per sample. Results are shown for AMR genes found on the
chromosome, and on plasmids. Perfect or Strict hits are categoties from RGI: perfect 
hits are 100% identical, while strict hits are not identidy, but close (based on 
curated cut off values).

```{r, echo = FALSE}

df$Cut_Off = factor(df$Cut_Off, levels=c("Perfect", "Strict"), ordered=TRUE)

table <-
  df %>%
  group_by(Sample, molecule_type, Cut_Off) %>%
  tally() %>%
  pivot_wider(names_from = c(molecule_type, Cut_Off),
              values_from = n, values_fill = 0,
              names_glue = "{molecule_type}: {Cut_Off}",
              names_expand = TRUE)

kable(table)

```

Number of plasmids detected per sample. 

```{r, echo=FALSE}

plasmids_df <-
  df %>%
  filter(molecule_type == "plasmid")

table <-
  plasmids_df %>%
  select(Sample, primary_cluster_id) %>%
  unique() %>%
  group_by(Sample) %>%
  tally()

kable(table)

```

## Plasmid details:

```{r, echo=FALSE, results='asis'}

# Which samples have plasmids?
samples_w_plasmids <- unique(plasmids_df$Sample)

# For each sample, print out the tables of the plasmid details, and the
# AMR genes found on each plasmid
for (sample in samples_w_plasmids){

  # Print out the current sample in the report
  cat("### Sample:", sample, "  \n", sep = " ")

  # Get curent sample
  sample_df <- plasmids_df %>% filter(Sample == sample)
  # Get the plasmids of the current sample
  plasmids <- unique(sample_df$primary_cluster_id)

  # Print out the tables
  for (plasmid in plasmids) {

    # Print out the current plasmid
    cat("Plasmid:", plasmid, "  \n", sep = " ")
    # Get the dataframe pertaining to the current plasmid
    plasmid_df <- sample_df %>% filter(primary_cluster_id  == plasmid)

    # Get the MOB-suite details of the current plasmid
    plasmid_info_table <-
      plasmid_df %>%
      select(primary_cluster_id,
             secondary_cluster_id,
             size,
             `rep_type(s)`,
             `relaxase_type(s)`,
             `orit_type(s)`,
             predicted_mobility) %>%
      unique()

    # Get the AMR genes of the current plasmid.
    plasmid_AMR_gene_table <-
      plasmid_df %>%
      select(Best_Hit_ARO,
             Cut_Off,
             Model_type,
             `Drug Class`,
             `Resistance Mechanism`,
             `AMR Gene Family`)

    # Create the tables to be formatted into the report.
    # Explicetely call print to work in for loops.
    print(kable(plasmid_info_table))
    print(kable(plasmid_AMR_gene_table))

  }
}
```

